\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-16 docs/paper/paper final.tex
Moved data acquisition to appendix A

%- Apply structure PC on resting-state functional time-series
%- Apply directional PC
Both standard PC and EMS-pc have been used to find brain connectivity.
The data which is used is functional time-series data, and it is the same as the data used in Hinne et al.\cite{hinne2013}, as described in Section~\ref{sec:data}.
This data is obtained from six subject.
From this data, covariance between regions can be determined, so that regions can be tested for \textit{d}-separation with the Fisher's conditional independence test.
This is required to use the PC algorithm.
First, the strucural part of the PC algorithm will be applied on the data.
This will result in a graph describing undirected connections between regions.
There is no difference between standard PC and EMS-PC in this result.
After that, the second part of the PC algorithm is run to orient edges in this graph.
This is different for standard PC and EMS-PC and a result will therefore be obtained for both algorithms.

@@

%- Parameter optimisation (model selection)
The experiments were run using an alpha-value of 0.01 for the independence test, and using 300 random permutations of the nodes per subject.
% TODO: Onvoldoende.

@@

% TODO: Move to appendix?
\subsection{Data acquisition}\label{sec:data}
%Subject acquisition and instruction
%Used equipment and specs
%Experimental setup
%Scanner settings
%Preprocessing
%- Software
%- Scripts
%Resulting data specs
%TODO niet helemaal happy, hoe zeg je dit zonder steeds "as described by Hinne et al." te zeggen? "This research" kan ook naar ons eigen werk verwijzen en is verwarrend, het moet duidelijk zijn dat dit alles niet door ons gedaan is.
We performed our analysis on the same data as treated by Hinne et al. in the aforementioned Bayesian structural analysis \cite{hinne2013, hinne2013structfunc}.
This article describes how resting-state functional data of six subjects was measured at the Donders Centre for Cognitive Neuroimaging at the Radboud University.
This functional data is divided in 116 nodes and 1029 time-series per subject.
Additionally, diffusion-weighted images of these subjects have been obtained.
Based on these DWI-measurements, a structural connectivity matrix has been inferred with a technique described by Hinne et al.
We used the six resulting resting-state functional time series data and connectivity matrices from the Bayesian analysis as pre-processed by Hinne et al.

@@

>>>>

%- Apply structure PC on resting-state functional time-series
%- Apply directional PC
We applied standard PC and EMS-PC on functional resting-state time-series data of six healthy individuals, also previously used by Hinne et al\cite{hinne2013}.
1030 volumes were obtained per subject.
After preprocessing the fMRI data was parcellated according to the Automated Anatomical Labeling (AAL) atlas in 116 regions of interest.
The exact procedure of subject acquisition, used scanner properties and parameters and data preprocessing is provided in appendix \ref{sec:data}.
We use Fisher's z-test for conditional independence to match the continuous nature of the data.

For all experiments we first apply part 1 of standard PC and EMS-PC on the data.
This will result in a graph describing undirected connections between regions.
For structure only the first found separating set is relevant, thus EMS-PC and standard PC return identical graph structure.
This structure is then oriented with part 2 of standard PC and EMS-PC given earlier found separating sets.
This procedure yields different orientations in theory.

@@

\paragraph{Parameter optimisation}
The experiments were run using an alpha-value of 0.01 for the independence test, and using 300 random permutations of the nodes per subject.
% TODO: Onvoldoende.

@@

@@

\appendix
\section{Data acquisition}\label{sec:data}
%Subject acquisition and instruction
%Used equipment and specs
%Experimental setup
%Scanner settings
%Preprocessing
%- Software
%- Scripts
%Resulting data specs
%TODO niet helemaal happy, hoe zeg je dit zonder steeds "as described by Hinne et al." te zeggen? "This research" kan ook naar ons eigen werk verwijzen en is verwarrend, het moet duidelijk zijn dat dit alles niet door ons gedaan is.
We performed our analysis on the same data as treated by Hinne et al. in the aforementioned Bayesian structural analysis \cite{hinne2013, hinne2013structfunc}.
This article describes how resting-state functional data of six subjects was measured at the Donders Centre for Cognitive Neuroimaging at the Radboud University.
This functional data is divided in 116 nodes and 1029 time-series per subject.
Additionally, diffusion-weighted images of these subjects have been obtained.
Based on these DWI-measurements, a structural connectivity matrix has been inferred with a technique described by Hinne et al.
We used the six resulting resting-state functional time series data and connectivity matrices from the Bayesian analysis as pre-processed by Hinne et al.
